Estimation below the detection limit

### 2018-05-02 TEX/draft2.tex
Including figures with new ROI
Updated experiment results for heterogeneous case and copied scripts to TEX folder

\begin{figure}[t]
	\centering
	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous/progressive_n10000000000_107521}
	\caption{\TODO{...}}
	\label{fig:1Dhomosignals}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous/progressive_RMSE_n10000000000_107521}
	\caption{\TODO{...}}
	\label{fig:1DhomoRMSE}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous_new_ROI/progressive_n10000000000_107521}
	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
	\label{fig:1Dhomosignals}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.7\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n10000000000_107521}
	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
	\label{fig:1DhomoRMSE}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{XP_1D_heterogeneous/data_example_heterogeneous_n_24600000000_604392_fig1}
\caption{\TODO{Thin yellow is ground truth; blue is ROI of first optimization; red is final estimation. Relative error for blue is .37, and .13 for red. Individual relative errors of the red estimates: 0.0239393 / 0.208925 / 0.0335956}}
\label{fig:1Dheterosignals}
\end{figure}
